### 2016-09-08 R/ITHIM.Rmd

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
library("devtools")
install_github("smbache/magrittr", ref="master")
library("magrittr")
install("~/ITHIM/")
library("ITHIM")
```

@@

```{r parsely, eval = TRUE}
convertToHHS <- function(states){
  HHSRegions <- matrix(c("CT","ME","MA","NH","RI","VT","NJ","NY","DE","DC","MD","PA","VA","WV","AL","FL","GA","KY","MS","NC","SC","TN","IL","IN","MI","MN","OH","WI","AR","LA","NM","OK","TX","IA","KS","MO","NE","CO","MT","ND","SD","UT","WY","AZ","CA","HI","NV","AK","ID","OR","WA",1,1,1,1,1,1,2,2,3,3,3,3,3,3,4,4,4,4,4,4,4,4,5,5,5,5,5,5,6,6,6,6,6,7,7,7,7,8,8,8,8,8,8,9,9,9,9,10,10,10,10,"HHS1","HHS1","HHS1","HHS1","HHS1","HHS1","HHS2","HHS2","HHS3","HHS3","HHS3","HHS3","HHS3","HHS3","HHS4","HHS4","HHS4","HHS4","HHS4","HHS4","HHS4","HHS4","HHS5","HHS5","HHS5","HHS5","HHS5","HHS5","HHS6","HHS6","HHS6","HHS6","HHS6","HHS7","HHS7","HHS7","HHS7","HHS8","HHS8","HHS8","HHS8","HHS8","HHS8","HHS9","HHS9","HHS9","HHS9","HHS10","HHS10","HHS10","HHS10"), nrow = 51, ncol = 3)
  StateToHHS <- HHSRegions[,3]
  names(StateToHHS) <- HHSRegions[,1]
  return(StateToHHS[states])
}

@@

## DAYV2PUB <- within(DAYV2PUB, {
##     URBRUR <- as.factor(URBRUR)
##     HHSTATE <- as.factor(HHSTATE)
##     MSACAT <- as.factor(MSACAT)
##     TRPTRANS <- as.factor(TRPTRANS)
##     TRPMILES <- as.numeric(TRPMILES)
## })

@@

```{r summary, fig.width = 20, fig.height = 10, eval = TRUE, echo = FALSE}
summary(with(subset(NHTS.trips, AT == "walk"), TRPMILES))
summary(with(subset(NHTS.trips, AT == "cycle"), TRPMILES))
summary(with(subset(NHTS.trips, AT == "other"), TRPMILES))
summary(with(subset(NHTS.trips, AT == "walk"), TRVL_MIN))
summary(with(subset(NHTS.trips, AT == "cycle"), TRVL_MIN))
summary(with(subset(NHTS.trips, AT == "other"), TRVL_MIN))

@@

g <- ggplot(D, aes(Speed, ..density.., fill = mode)) + geom_histogram(breaks = seq(0,25,1)) + theme_bw() + scale_x_continuous(name="Speed") + scale_y_continuous(name="Density") + facet_grid(. ~ mode)
g

@@

```{r subset, eval = TRUE, fig.width = 10, echo = FALSE}
NHTS.person <- subset( NHTS.person, MSA == TRUE )
NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"))
barplot(with(NHTS,table(HHS)))
```

@@

```{r natl}
listOfLists <- lapply(split(NHTS, NHTS$SEX),function(x) split(x, x$AGE))
counts <- lapply(listOfLists, function(x) lapply(x, countPeople))
walkLength <- lapply(listOfLists, function(x) lapply( x, tripTime, mode = "walk"))
cycleLength <- lapply(listOfLists, function(x) lapply( x, tripTime, mode = "cycle"))

@@

```{r suppressed, eval = TRUE, echo = FALSE}
wonder <- within( wonder, {
    newDeaths <- as.numeric(ifelse(deaths5yr == "Suppressed", sample(0:9), as.numeric(as.character(deaths5yr))))
    })
```

@@

```{r parameters, eval = TRUE, echo = FALSE}
(parameters <- ddply(D, .(SEX, AGECAT), summarise,
             mean = mean(METs, na.rm=T),
             sd = sd(METs, na.rm=T)
             ))

METmatrix <- rbind(matrix(0,nrow = 2, ncol = 2), matrix(parameters$mean, ncol = 2))
(METmatrix <- METmatrix/METmatrix[3,2])
```

@@

```{r ITHIMObjs, eval = TRUE, fig.width = 20, fig.height = 10, echo = FALSE}
compute <- TRUE

@@

for( muNonTravel in seq(1,75,length.out = 3) ){

@@

  for (HHS in paste0("HHS",1:10)){
    ITHIMList[[HHS]] <- ITHIM.default
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "muwt", muwtList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "muct", muctList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "Rwt", RwtList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "Rct", RctList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "GBD", GBDList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "muNonTravel", muNonTravel)
  }

  ITHIM.national <- createITHIM(vision = "baseline", region = "national")
  ITHIM.national <- updateITHIM(ITHIM.national, "muNonTravel", muNonTravel)
  ITHIM.national <- updateITHIM(ITHIM.national, "muwt", muwtNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "muct", muctNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "Rwt", RwtNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "Rct", RctNational)
  DALYs <- lapply(ITHIMList, sumDALY, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(HHS = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}
}else{
DALYsTotal <- readRDS(file = "./data/DALYsTotal.rds")
}
p <- ggplot(DALYsTotal, aes(x = muNonTravel, y = DALY, colour = HHS))
p  + geom_line() + theme_bw() + scale_x_continuous(name="Non-Travel METs mean") + scale_y_continuous(name="Change in DALY (National)") + facet_grid(. ~ HHS)
```

@@

```{r CRA, eval = TRUE, echo = FALSE}

CRA.fn <- function(i, j){
  foo <- compareModels( ITHIMList[[i]], ITHIMList[[j]])
  sum(unlist(foo$AF))
}

CRAMatrix <- matrix(NA, nrow = 10, ncol = 10)

for( i in 1:10 ){
  CRA <- c()
  for( j in 1:10 ){
    CRA <- c( CRA, CRA.fn(i, j))
  }
  CRAMatrix[i,] <- CRA
}

which(CRAMatrix == max(CRAMatrix), arr.ind = TRUE)

## DETAILS ON WONDER QUERY

>>>>

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
library("devtools")
install_github("smbache/magrittr", ref="master")
library("magrittr")
install("~/ITHIM/")
library("ITHIM")
```

@@

```{r parsely, eval = TRUE, echo = FALSE}
convertToHHS <- function(states){
  HHSRegions <- matrix(c("CT","ME","MA","NH","RI","VT","NJ","NY","DE","DC","MD","PA","VA","WV","AL","FL","GA","KY","MS","NC","SC","TN","IL","IN","MI","MN","OH","WI","AR","LA","NM","OK","TX","IA","KS","MO","NE","CO","MT","ND","SD","UT","WY","AZ","CA","HI","NV","AK","ID","OR","WA",1,1,1,1,1,1,2,2,3,3,3,3,3,3,4,4,4,4,4,4,4,4,5,5,5,5,5,5,6,6,6,6,6,7,7,7,7,8,8,8,8,8,8,9,9,9,9,10,10,10,10,"HHS01","HHS01","HHS01","HHS01","HHS01","HHS01","HHS02","HHS02","HHS03","HHS03","HHS03","HHS03","HHS03","HHS03","HHS04","HHS04","HHS04","HHS04","HHS04","HHS04","HHS04","HHS04","HHS05","HHS05","HHS05","HHS05","HHS05","HHS05","HHS06","HHS06","HHS06","HHS06","HHS06","HHS07","HHS07","HHS07","HHS07","HHS08","HHS08","HHS08","HHS08","HHS08","HHS08","HHS09","HHS09","HHS09","HHS09","HHS10","HHS10","HHS10","HHS10"), nrow = 51, ncol = 3)
  StateToHHS <- HHSRegions[,3]
  names(StateToHHS) <- HHSRegions[,1]
  return(StateToHHS[states])
}

@@

@@

```{r summary, fig.width = 20, fig.height = 10, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
#summary(with(subset(NHTS.trips, AT == "walk"), TRPMILES))
#summary(with(subset(NHTS.trips, AT == "cycle"), TRPMILES))
#summary(with(subset(NHTS.trips, AT == "other"), TRPMILES))
#summary(with(subset(NHTS.trips, AT == "walk"), TRVL_MIN))
#summary(with(subset(NHTS.trips, AT == "cycle"), TRVL_MIN))
#summary(with(subset(NHTS.trips, AT == "other"), TRVL_MIN))

@@

g <- ggplot(D, aes(Speed, ..density.., fill = mode)) + geom_histogram() + theme_bw() + scale_x_continuous(name="Speed") + scale_y_continuous(name="Density") + facet_grid(. ~ mode, scales = "free")
g

@@

How do we merge?  Are there people who were surveyed who had zero
travel time?  Couldnt have been very many.  But I think there are
people in the PERSON table that were not interviewed.

```{r subset, eval = TRUE, fig.width = 10, echo = FALSE}
NHTS.person <- subset( NHTS.person, MSA == TRUE )
NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"))
```

@@

```{r natl, eval = TRUE, echo = FALSE, warning = FALSE}
listOfLists <- lapply(split(NHTS, NHTS$SEX),function(x) split(x, x$AGE))
counts <- lapply(listOfLists, function(x) lapply(x, countPeople))
walkLength <- lapply(listOfLists, function(x) lapply( x, tripTime, mode = "walk"))
cycleLength <- lapply(listOfLists, function(x) lapply( x, tripTime, mode = "cycle"))

@@

```{r suppressed, eval = TRUE, echo = FALSE, warning = FALSE}
wonder <- within( wonder, {
    newDeaths <- as.numeric(ifelse(deaths5yr == "Suppressed", sample(0:9), as.numeric(as.character(deaths5yr))))
    })
```

@@

```{r parameters, eval = TRUE, echo = FALSE}
parameters <- ddply(D, .(SEX, AGECAT), summarise,
             mean = mean(METs, na.rm=T),
             sd = sd(METs, na.rm=T)
             )

METmatrix <- rbind(matrix(0,nrow = 2, ncol = 2), matrix(parameters$mean, ncol = 2))
METmatrix <- METmatrix/METmatrix[3,2]
```

@@

```{r ITHIMObjs, eval = TRUE, fig.width = 20, fig.height = 10, echo = FALSE, warning = FALSE}
compute <- TRUE

@@

for( muNonTravel in seq(1,50,length.out = 20) ){

@@

  for (HHS in c(paste0("HHS0",1:9),"HHS10")){
    ITHIMList[[HHS]] <- ITHIM.default
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "muwt", muwtList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "muct", muctList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "Rwt", RwtList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "Rct", RctList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "GBD", GBDList[[HHS]])
    ITHIMList[[HHS]] <- updateITHIM(ITHIMList[[HHS]], "muNonTravel", muNonTravel)
  }

  ITHIM.national <- createITHIM(vision = "baseline", region = "national")
  ITHIM.national <- updateITHIM(ITHIM.national, "muNonTravel", muNonTravel)
  ITHIM.national <- updateITHIM(ITHIM.national, "muwt", muwtNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "muct", muctNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "Rwt", RwtNational)
  ITHIM.national <- updateITHIM(ITHIM.national, "Rct", RctNational)
  DALYs <- lapply(ITHIMList, sumDALY, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(HHS = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}

}else{
  DALYsTotal <- readRDS(file = "./data/DALYsTotal.rds")
}

barplot(with(NHTS,table(HHS)))
p <- ggplot(DALYsTotal, aes(x = muNonTravel, y = DALY, colour = HHS))
p  + geom_line(size = 2) + theme_bw() + scale_x_continuous(name="Non-Travel METs mean") + scale_y_continuous(name="Change in DALY (National)") + facet_grid(. ~ HHS)
```

@@

```
# Appendix

### DETAILS ON WONDER QUERY
